\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction} % include in the table of contents
\markboth{General Introduction}{}

Digital news consumption in Tunisia has grown steadily, but the outlets that produce it (\textit{La Presse}, \textit{Business News}, \textit{Kapitalis}, \textit{Mosaïque FM}, and others) remain as fragmented online as they are in print: each publishes independently, mixes French with Arabic-language content, and offers no shared index. A reader who wants a cross-source view of the day's news, or an analyst who wants to track how a topic or a region is covered over time, has no single place to look and no automated way to search, summarize, or ask questions of that content.

News Insight addresses this gap with an MLOps platform built around three verbs: \emph{scrape}, \emph{analyse}, \emph{explore}. It continuously collects articles from multiple Tunisian sources, enriches them with multilingual embeddings, sentiment analysis, and unsupervised topic modelling, and adds a generative-AI layer (summaries, human-readable topic labels, and a retrieval-augmented "ask the news" chat assistant) on top. The whole pipeline is orchestrated, tracked, and containerized so it can be run and reproduced end to end, not just as a one-off analysis. The platform is developed as an End-of-Semester Project in Data Science and AI, academic year 2025-2026, by a three-person student team.

This report is organized into eleven chapters. Chapter 1 sets out the project's context, problem statement, objectives, work methodology, and technology stack. Chapter 2 presents the global architecture, including the use case, class, and sequence views of the system. Chapters 3 and 4 cover the data layer: web scraping and ingestion, then the PostgreSQL and pgvector storage design. Chapter 5 details the machine learning and NLP pipeline (embeddings, sentiment, BERTopic topic modelling), and Chapter 6 the GenAI features built on top of it (summaries, topic labels, semantic search, and the chat assistant). Chapter 7 describes how the pipeline is orchestrated with Prefect and tracked with MLflow. Chapter 8 documents the FastAPI backend that exposes the data, Chapter 9 the Docker-based deployment, and Chapter 10 the React frontend through which the platform is explored. Chapter 11 closes the report with a summary of the project's contributions, its current limitations, and the improvements planned for future iterations.