\chapter*{Webography}
\addcontentsline{toc}{chapter}{Webography}
\markboth{Webography}{}
\stepcounter{chapter}

\begin{sloppypar}
\begin{itemize}
    \item FastAPI. \textit{FastAPI Documentation}. \url{https://fastapi.tiangolo.com/}
    \item Prefect Technologies, Inc. \textit{Prefect Documentation}. \url{https://docs.prefect.io/}
    \item MLflow Project, Linux Foundation AI \& Data. \textit{MLflow Documentation}. \url{https://mlflow.org/docs/latest/index.html}
    \item Maarten Grootendorst. \textit{BERTopic Documentation}. \url{https://maartengr.github.io/BERTopic/}
    \item Hugging Face. \textit{Sentence Transformers Documentation}. \url{https://www.sbert.net/}
    \item pgvector contributors. \textit{pgvector: Open-Source Vector Similarity Search for Postgres}. \url{https://github.com/pgvector/pgvector}
    \item PostgreSQL Global Development Group. \textit{PostgreSQL Documentation}. \url{https://www.postgresql.org/docs/}
    \item Meta Platforms, Inc. \textit{React Documentation}. \url{https://react.dev/}
    \item Vite core team. \textit{Vite Documentation}. \url{https://vite.dev/}
    \item Docker Inc. \textit{Docker Compose Documentation}. \url{https://docs.docker.com/compose/}
    \item Groq Inc. \textit{GroqCloud API Documentation}. \url{https://console.groq.com/docs/}
    \item Kurt McKee et al. \textit{feedparser Documentation}. \url{https://feedparser.readthedocs.io/}
    \item Leonard Richardson. \textit{Beautiful Soup Documentation}. \url{https://www.crummy.com/software/BeautifulSoup/bs4/doc/}
    \item Explosion AI. \textit{spaCy Documentation}. \url{https://spacy.io/}
    \item Recharts Group. \textit{Recharts Documentation}. \url{https://recharts.org/}
    \item D3 contributors. \textit{d3-geo Documentation}. \url{https://d3js.org/d3-geo}
\end{itemize}
\end{sloppypar}
